When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote NASA effort H1c

The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`).
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
The median RT did not differ between 2-back and 4-back, and the median RT was higher for 3-back than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

@@

>>>>

The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level, apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level, apa_print(hypothesis1b_BF)$statistic`).
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
The median RT did not differ between 2-back and 4-back, and the median RT was higher for 3-back than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

@@

All NASA-TLX subscale scores increased across *n*-back levels.
The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level, apa_print(hypothesis1c_effort__BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2, apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4, apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
